---
title: "Covariates"
author: "Chelsea Harmon"
date: "12/28/2017, updated 1/28/2019"
output: html_document
---

---
title: "Making group level covariates"
author: "Michelle.VanTieghem"
date: "Feb 10 2017"
output: html_document
---

# pull the data from master database! 

```{r, echo = FALSE}
#setwd ("/Volumes/danl/SB/DTI/scripts/covariates_scripts/")
setwd("/Users/chelseaharmon/Columbia/danlab/DTI/data/")
#output.directory <- ("~/Volumes/danl/SB/DTI/scripts/covariates_scripts/")
output.directory <- ("~/Columbia/danlab/DTI/covariatesFiles/")

# get master data.
full.df.master <- read.csv("~/Columbia/danlab/SB/Data_Entry_Master/J.Data_Entry_Master_3.14.2017_fixed_fixed.csv")
full.df.master$SUB_ID <- full.df.master$IDENT_SUBID
nrow(full.df.master)
full.df.master$GROUP <- full.df.master$IDENT_SUBTYPE

# get final sublist from all of your exclusion AND with Cortisol, N 59 
# from your cross_sectionalData
cross.data <- read.csv("~/Columbia/danlab/DTI/data/tbss_cross_over8_motionExcluded_1_2_2018.csv")
nrow(cross.data)
head(cross.data)
#cross.data$GROUP <- full.df.master$IDENT_SUBTYPE
long.data <- read.csv("~/Columbia/danlab/DTI/data/tbss_long_over8_motionExcluded_1_25_2018.csv")   # old 11_28_2017.csv

nrow(long.data)
head(long.data)
#long.data$GROUP <- full.df.master$IDENT_SUBTYPE
```

# Making covariate files with Cross Sectional Dataset
```{r, echo = FALSE}
# checking age variable... should be identical! 
max(cross.data$GROUP.PI, na.rm=TRUE)
cross.data$GROUP.PI <- cross.data$GROUP
cross.data$GROUP.COMP <- ifelse(cross.data$GROUP == 1, 0, ifelse(cross.data$GROUP == 0, 1, NA))
#full.df.master$Age_Mos_Matching <- full.df.master$SUBAGE_session2
cross.data$gender <- cross.data$DEM_3_GENDER_CHILD
cross.data$age <- cross.data$MeanCenteredAge
max(cross.data$GROUP.PI, na.rm=TRUE)
max(cross.data$GROUP.COMP, na.rm=TRUE)
max(cross.data$gender, na.rm=TRUE)
max(cross.data$age, na.rm=TRUE)

#full.df.master$gender <- full.df.master$DEM_3_GENDER_CHILD

covariates <- data.frame(cross.data$SUB_IDENT, cross.data$GROUP.PI, cross.data$GROUP.COMP, cross.data$age, cross.data$gender)
names(covariates) <- cbind("SUB_IDENT", "GROUP.PI", "GROUP.COMP", "age", "sex")
```

# Making covariate files with Longitudinal data set
```{r, echo = FALSE}
# checking age variable... should be identical! 
max(long.data$GROUP.PI, na.rm=TRUE)
long.data$GROUP.PI <- long.data$GROUP
long.data$GROUP.COMP <- ifelse(long.data$GROUP == 1, 0, ifelse(long.data$GROUP == 0, 1, NA))

#full.df.master$Age_Mos_Matching <- full.df.master$SUBAGE_session2
long.data$gender <- long.data$DEM_3_GENDER_CHILD
long.data$age <- long.data$MeanCenteredAge
max(long.data$GROUP.PI, na.rm=TRUE)
max(long.data$GROUP.COMP, na.rm=TRUE)
#max(long.data$gender, na.rm=TRUE)

full.df.master$idnum_long <- as.character(full.df.master$IDENT_SUBID)
sub <- full.df.master[ , c("idnum_long","IDENT_SUBTYPE", "SUBAGE_session2", "SUBAGE_session3", "SUBAGE_session4", "DEM_3_GENDER_CHILD")]

# convert into a long dataset by wave, repeating AGE
library(dplyr)
library(tidyverse)
sub_long <- gather(sub, Session, Age, SUBAGE_session2:SUBAGE_session4)

# make a long-version of this ID number. we will use this to merge with fsdata.
sub_long$SUBJECTID_long <- ifelse(sub_long$Session == "SUBAGE_session3", paste0(sub_long$idnum_long, "_fu1"), ifelse(sub_long$Session == "SUBAGE_session4", paste0(sub_long$idnum_long, "_fu2"), sub_long$idnum_long))

long.data<- merge(long.data, sub_long, by="SUBJECTID_long")
long.data$gender <- long.data$DEM_3_GENDER_CHILD

#full.df.master$gender <- full.df.master$DEM_3_GENDER_CHILD

covariates <- data.frame(long.data$SUB_IDENT, long.data$GROUP.PI, long.data$GROUP.COMP, long.data$age, long.data$gender)
names(covariates) <- cbind("SUB_IDENT", "GROUP.PI", "GROUP.COMP", "age", "sex")
```

### WRITING CrossSecional COVARIATE FILES
```{r, echo = FALSE}
# write this one... as a check of SUBJECTID order
file.name <- paste0(output.directory, "cross_covariates_withnames.txt")
write.table(covariates, file.name, quote = FALSE, na = "", row.names = FALSE)
ncol(covariates)
# then get rid of subject ID for copy paste into FSL 
covariate.file <- covariates[,2:5]
max(covariate.file, na.rm=TRUE)
#View(covariate.file)
file.name <- paste0(output.directory, "cross_covariates.txt")
write.table(covariate.file, file.name, quote = FALSE, na = "", row.names = FALSE)
```

### WRITING Longitudinal COVARIATE FILES
```{r, echo = FALSE}
# write this one... as a check of SUBJECTID order
file.name <- paste0(output.directory, "long_covariates_withnames01.28.2019.txt")
write.table(covariates, file.name, quote = FALSE, na = "", row.names = FALSE)
ncol(covariates)
# then get rid of subject ID for copy paste into FSL 
covariate.file <- covariates[,2:5]
max(covariate.file, na.rm=TRUE)
#View(covariate.file)
file.name <- paste0(output.directory, "long_covariates_01.28.2019.txt")
write.table(covariate.file, file.name, quote = FALSE, na = "", row.names = FALSE)
```





### making group X age interaction Crosseciontal 
```{r, echo = FALSE}
covariate.file$PIxAge <- covariate.file$age*covariate.file$GROUP.PI
covariate.file$CompxAge <- covariate.file$age*covariate.file$GROUP.COMP

covariate.file.int <- data.frame(cross.data$GROUP.PI, cross.data$GROUP.COMP, covariate.file$PIxAge, covariate.file$CompxAge, cross.data$gender)
#could possibly add age by itself here before gender (above)
names(covariate.file.int) <- cbind("GROUP.PI", "GROUP.COMP", "PIxAge", "COMPxAge", "sex")
head(covariate.file.int)
file.name <- paste0(output.directory, "cross_covariates_GroupxAge.txt")
write.table(covariate.file.int, file.name, quote= FALSE, row.names = FALSE)
ncol(covariate.file.int)
```


### making group X CORT interaction Longitduinal
```{r, echo = FALSE}
covariate.file$PIxAge <- covariate.file$age*covariate.file$GROUP.PI
covariate.file$CompxAge <- covariate.file$age*covariate.file$GROUP.COMP

covariate.file.int <- data.frame(long.data$GROUP.PI, long.data$GROUP.COMP, covariate.file$PIxAge, covariate.file$CompxAge, long.data$gender)
#could possibly add age by itself here before gender (above)
names(covariate.file.int) <- cbind("GROUP.PI", "GROUP.COMP", "PIxAge", "COMPxAge", "sex")
head(covariate.file.int)
file.name <- paste0(output.directory, "long_covariates_GroupxAge01.28.2019.txt")
write.table(covariate.file.int, file.name, quote= FALSE, row.names = FALSE)
ncol(covariate.file.int)
```


